AGB Stars in the IR: Physical Characteristics, Galactic Spatial Distribution, and Chemical Impact of the Milky Way AGB Population

### 2014-11-08 thesispropbody_d1.tex
Update 11/7/2014

Once a candidate sample has been retrieved from the ALLWISE-2MASS database matching our broad color criteria, we narrow them into high-photometric-quality O-rich and C-rich populations using the same criteria from \cite{2014MNRAS.442.3361N}. Assuming absolute magnitudes based upon the aforementioned color-magnitude relationships, we simultaneously estimate the distance and coefficient for dust extinction along the line of sight for each star using {\tt GALFASTDUST}, which includes the dust maps of .

@@

\section{Timeline}
\begin{enumerate}
\item Publish current results of AGB candidate catalog and Galactic distribution discussed in section~\ref{sec:completedWork}, with publicly accessible data -- Q1 2015.
\item Investigating unclassified AGB candidates -- Q1 2015
\item Comparison with {\tt TRILEGAL} -- Q2-Q3 2015.
\item Estimates of stellar parameters from APOGEE -- Q1 2016.
\item Publish results of comparisons and estimates from {\tt TRILEGAL} and APOGEE -- Q2-Q3 2016
\item Defense -- Q3-Q4 2016
\end{enumerate}

>>>>

Once a candidate sample has been retrieved from the ALLWISE-2MASS database matching our broad color criteria, we narrow them into high-photometric-quality O-rich and C-rich populations using the same criteria from \cite{2014MNRAS.442.3361N}. Assuming absolute magnitudes based upon the aforementioned color-magnitude relationships, we simultaneously estimate the distance and coefficient for dust extinction along the line of sight for each star using {\tt GALFASTDUST}.

@@

\section{Timeline}
\begin{enumerate}
\item Paper 1: Publication of AGB candidate catalog and preliminary measurements of Milky Way disk and bulge -- \textbf{End of March 2015}
	\begin{itemize}
		\item Sample selection completeness and contamination estimates
		\item O-rich/C-rich classification from color-color criteria
		\item Identification of unclassified candidates
		\item Estimates of unconfirmed classifications with Gaussian Mixture Models
		\item Measurements of disk scale height/length
		\item Measurements of the sizes of the Galactic bar \& bulge and orientation of the Galactic bar
		\item Measurement of radius of Galactic disk
	\end{itemize}

\item Paper 2: Characteristics of the Milky Way galaxy via ALLWISE AGB candidates -- \textbf{End of Sept 2015}
	\begin{itemize}
		\item Mass-loss rate, model metallicity, temperature, size, and age of AGB candidates with respect to position
		\item Interpretations of position-dependent characteristics
		\item Meaning of these results with respect to improvements in AGB evolutionary tracks
	\end{itemize}

\item Post doctorate and Job Applications -- \textbf{Oct-Nov 2015}
\item Paper 3: AGB stellar parameters from APOGEE and extrapolation to entire candidate sample -- \textbf{May 2016}
	\begin{itemize}
		\item Matches between ALLWISE candidates and APOGEE targets
		\item Color-parameter relationships between APOGEE and ALLWISE
		\item Extrapolation to entire candidate sample through color-parameter relationships
		\item Comparison to estimations from various machine-learning techniques
		\item Comparison to estimations from TRILEGAL
	\end{itemize}
\item Dissertation preparation -- \textbf{June - August 2016}
\item Defense -- \textbf{August/September 2016}
\end{enumerate}
